### 2017-09-29 README.Rmd

## Use

### Doubly-robust inference for average treatment effect

Suppose the data consist of a vector of baseline covariates (`W`), a multi-level treatment assignment (`A`), and a continuous or binary-valued outcome (`Y`). The function `drtmle` may be used to estimate $E[E(Y | A=a_0, W)]$ for user-selected values of $a_0$ (via option `a_0`). The resulting targeted minimum loss-based estimates are doubly robust with respect to both consistency and asymptotic normality. The function computes doubly robust covariance estimates that can be used to construct doubly robust confidence intervals for marginal means and contrasts between means. A simple example on simulated data is shown below. We refer users to the vignette for more information and further examples.

@@

# estimate the covariate-adjusted marginal mean for A = 1 and A = 0
# here, we do not properly estimate the propensity score
fit1 <- drtmle(W = W, A = A, Y = Y, # input data
              a_0 = c(0,1), # return estimates for A = 0 and A = 1
              SL_Q = "SL.npreg", # use kernel regression for E(Y | A=a, W)
              glm_g = "W1 + W2", # use misspecified main terms glm for E(A | W)
              SL_Qr = "SL.npreg", # use kernel regression to guard against
              					  # misspecification of outcome regression
              SL_gr = "SL.npreg" # use kernel regression to guard against 
              					 # misspecification of propensity score
              )
# print the output
fit1

@@

# get confidence intervals for ate
ci_ate1 <- ci(fit1,contrast = c(-1,1))
# print the output
ci_ate1
```

@@

```{r}
# fit iptw 
fit2 <- adaptive_iptw(Y = Y, A = A, W = W, a_0 = c(0,1),
               SL_g = c("SL.glm","SL.mean","SL.step.interaction"),
               SL_Qr = "SL.npreg")
# print the output
fit2

@@

# compute a confidence interval for the ate
ci_ate2 <- ci(fit2, contrast = c(-1,1))
# print the output
ci_ate2
```
---

>>>>

## Usage

### Doubly-robust inference for the average treatment effect

Suppose the data consist of a vector of baseline covariates (`W`), a multi-level
treatment assignment (`A`), and a continuous or binary-valued outcome (`Y`). The
function `drtmle` may be used to estimate $E[E(Y \mid A = a_0, W)]$ for
user-selected values of $a_0$ (via option `a_0`). The resulting targeted minimum
loss-based estimates are doubly robust with respect to both consistency and
asymptotic normality. The function computes doubly robust covariance estimates
that can be used to construct doubly robust confidence intervals for marginal
means and contrasts between means. A simple example on simulated data is shown
below. We refer users to the vignette for more information and further examples.

@@

# estimate the covariate-adjusted marginal mean for A = 1 and A = 0
# here, we do not properly estimate the propensity score
fit1 <- drtmle(W = W, A = A, Y = Y, # input data
               a_0 = c(0, 1), # return estimates for A = 0 and A = 1
               SL_Q = "SL.npreg", # use kernel regression for E(Y | A = a, W)
               glm_g = "W1 + W2", # use misspecified main terms glm for E(A | W)
               SL_Qr = "SL.npreg", # use kernel regression to guard against
                                   # misspecification of outcome regression
               SL_gr = "SL.npreg" # use kernel regression to guard against
                                  # misspecification of propensity score
              )
# print the output
fit1

@@

# get confidence intervals for ate
ci_ate1 <- ci(fit1,contrast = c(-1, 1))
# print the output
ci_ate1
```

@@

```{r}
# fit iptw
fit2 <- adaptive_iptw(Y = Y, A = A, W = W, a_0 = c(0, 1),
                      SL_g = c("SL.glm", "SL.mean", "SL.step.interaction"),
                      SL_Qr = "SL.npreg")
# print the output
fit2

@@

# compute a confidence interval for the ate
ci_ate2 <- ci(fit2, contrast = c(-1, 1))
# print the output
ci_ate2
```
---
